### 2014-03-03 seminar/seminar_report/chapter5.tex
changes

In this report, we presented research problems and questions we
aim to address in the thesis and proposed some preliminary results
about a cooperative game theory-based model for the aggregation of
web services within communities. The goal of our services is to
maximize efficiency by collaborating and forming stable
coalitions. Our method considers stability and fairness for all
web services within a community and offers an applicable mechanism
for membership requests and selection of web services. The
ultimate goal is to increase revenue by improving user
satisfaction, which comes from the ability to perform more tasks
with high quality. Simulation results show that our approximation
algorithms are polynomial in complexity and provide web services
and community owners with applicable and near-optimal decision
making mechanisms.

@@

>>>>

In this report, we proposed a cooperative game theory based model for the aggregation of web services within communities.
The goal of our services is to maximize efficiency by collaborating and forming stable
coalitions. Our method considers stability and fairness for all
web services within a community and offers an applicable mechanism
for membership requests and selection of web services. The
ultimate goal is to increase revenue by improving user
satisfaction, which comes from the ability to perform more tasks
with high quality. Simulation results show that our approximation
algorithms are polynomial in complexity and provide web services
and community owners with applicable and near-optimal decision
making mechanisms.

@@

\begin{center}
    \begin{tabular}{ | l | l | p{5cm} |}
    \hline
    Term & Activity & Publication \\ \hline
    Winter 2014 & 1 & 1 \\ \hline
    Summer 2014 & 1 & 1 \\ \hline
    Fall 2014 & 1 & 1 \\ \hline
    Winter 2015 & 1 & 1 \\
    \hline
    \end{tabular}
\end{center}
